A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-12 main.tex

  % 多段階計算のルール
  The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp\ are rules for a multi-stage calculus.
  They are corresponding to quoting a code, unquoting a code, making a stage abstraction, 
  application of $\epsilon$ stage to a stage abstraction, and cross-stage persistence, respectively.
  Please check Hanada and Igarashi \cite{Hanada2014} and Tsukada and Igarashi \cite{Tsukada} for details of these rules.

  % \TConv
  The main technical point of this paper is \TConv\ and type equivalence rules needed by \TConv.
  This rule allows ut to replace a type with another type that is equivalent.
  In a type system which includes dependent types, this kind of rule is essential
  because two types which have different shapes may be equivalent.
  For example, when we use a matrix type which have their sizes ($\textrm{Mat}\ n\ m$),
  $\textrm{Mat}\ 5\ 3$ is equivalent to $\textrm{Mat}\ (4+1)\ (1+2)$ obviously.

@@

  % \section{First Section}
  % \subsection{A Subsection Sample}
  % Please note that the first paragraph of a section or subsection is
  % not indented. The first paragraph that follows a table, figure,
  % equation etc. does not need an indent, either.
  % 
  % Subsequent paragraphs, however, are indented.
  % 
  % \subsubsection{Sample Heading (Third Level)} Only two levels of
  % headings should be numbered. Lower level headings remain unnumbered;
  % they are formatted as run-in headings.
  % 
  % \paragraph{Sample Heading (Fourth Level)}
  % The contribution should contain no more than four levels of
  % headings. Table~\ref{tab1} gives a summary of all heading levels.
  % 
  % \begin{table}
  % \caption{Table captions should be placed above the
  % tables.}\label{tab1}
  % \begin{tabular}{|l|l|l|}
  % \hline
  % Heading level &  Example & Font size and style\\
  % \hline
  % Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
  % 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
  % 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
  % 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
  % 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
  % \hline
  % \end{tabular}
  % \end{table}
  % 
  % 
  % \noindent Displayed equations are centered and set on a separate
  % line.
  % \begin{equation}
  % x + y = z
  % \end{equation}
  % Please try to avoid rasterized images for line-art diagrams and
  % schemas. Whenever possible, use vector graphics instead (see
  % Fig.~\ref{fig1}).
  % 
  % \begin{figure}
  % \includegraphics[width=\textwidth]{fig1.eps}
  % \caption{A figure caption is always placed below the illustration.
  % Please note that short captions are centered, while long ones are
  % justified by the macro package automatically.} \label{fig1}
  % \end{figure}
  % 
  % \begin{theorem}
  % This is a sample theorem. The run-in heading is set in bold, while
  % the following text appears in italics. Definitions, lemmas,
  % propositions, and corollaries are styled the same way.
  % \end{theorem}
  % %
  % % the environments 'definition', 'lemma', 'proposition', 'corollary',
  % % 'remark', and 'example' are defined in the LLNCS documentclass as well.
  % %
  % \begin{proof}
  % Proofs, examples, and remarks have the initial word in italics,
  % while the following text appears in normal font.
  % \end{proof}
  % For citations of references, we prefer the use of square brackets
  % and consecutive numbers. Citations using labels or the author/year
  % convention are also acceptable. The following bibliography provides
  % a sample reference list with entries for journal
  % articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
  % book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
  % and a homepage~\cite{ref_url1}. Multiple citations are grouped
  % \cite{ref_article1,ref_lncs1,ref_book1},
  % \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
  %
  % ---- Bibliography ----
  %
  % BibTeX users should specify bibliography style 'splncs04'.
  % References will then be sorted and formatted in the correct style.
  %
  \bibliographystyle{splncs04}
  \bibliography{main}
  %
  % \begin{thebibliography}{8}
  % \bibitem{ref_article1}
  % Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
  % 
  % \bibitem{ref_lncs1}
  % Author, F., Author, S.: Title of a proceedings paper. In: Editor,
  % F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
  % Springer, Heidelberg (2016). \doi{10.10007/1234567890}
  % 
  % \bibitem{ref_book1}
  % Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
  % Location (1999)
  % 
  % \bibitem{ref_proc1}
  % Author, A.-B.: Contribution title. In: 9th International Proceedings
  % on Proceedings, pp. 1--2. Publisher, Location (2010)
  % 
  % \bibitem{ref_url1}
  % LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
  % Oct 2017
  % \end{thebibliography}

>>>>

% Typing rules for a multi-stage calculus
The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp\ are rules for a multi-stage calculus.
They are corresponding to brackets, escape, making a stage abstraction, 
application of $\epsilon$ stage to a stage abstraction, and cross-stage persistence, respectively.
Please check Hanada and Igarashi \cite{Hanada2014} and Tsukada and Igarashi \cite{Tsukada} for details of these rules.

% \TConv
The main technical point of this paper is \TConv\ and type equivalence rules needed by \TConv.
This rule allows us to replace a type with another type that is equivalent.
In a type system which includes dependent types, this kind of rule is essential
because two types which have different shapes may be equivalent.
For example, when we use a vector type with its size ($\textrm{Vector}\ n$),
$\textrm{Vector}\ 5$ is equivalent to $\textrm{Vector}\ (4+1)$ obviously although they are not equivalent in apparently.

@@

% 2つの設計手法と今回採用した理由
% Conclusion送りか?
% When we design type equivalence rules of \LMD, there are two design choices.
% One is defining type equivalence by $\beta$-equality after we define $\beta$-reduction of types.
% Another is defining type equivalence directly by a combination of type equivalence rules.
% We adopt the latter one because it is convenient to handle CSP in the type equivalence.

% \section{First Section}
% \subsection{A Subsection Sample}
% Please note that the first paragraph of a section or subsection is
% not indented. The first paragraph that follows a table, figure,
% equation etc. does not need an indent, either.
% 
% Subsequent paragraphs, however, are indented.
% 
% \subsubsection{Sample Heading (Third Level)} Only two levels of
% headings should be numbered. Lower level headings remain unnumbered;
% they are formatted as run-in headings.
% 
% \paragraph{Sample Heading (Fourth Level)}
% The contribution should contain no more than four levels of
% headings. Table~\ref{tab1} gives a summary of all heading levels.
% 
% \begin{table}
% \caption{Table captions should be placed above the
% tables.}\label{tab1}
% \begin{tabular}{|l|l|l|}
% \hline
% Heading level &  Example & Font size and style\\
% \hline
% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
% \hline
% \end{tabular}
% \end{table}
% 
% 
% \noindent Displayed equations are centered and set on a separate
% line.
% \begin{equation}
% x + y = z
% \end{equation}
% Please try to avoid rasterized images for line-art diagrams and
% schemas. Whenever possible, use vector graphics instead (see
% Fig.~\ref{fig1}).
% 
% \begin{figure}
% \includegraphics[width=\textwidth]{fig1.eps}
% \caption{A figure caption is always placed below the illustration.
% Please note that short captions are centered, while long ones are
% justified by the macro package automatically.} \label{fig1}
% \end{figure}
% 
% \begin{theorem}
% This is a sample theorem. The run-in heading is set in bold, while
% the following text appears in italics. Definitions, lemmas,
% propositions, and corollaries are styled the same way.
% \end{theorem}
% %
% % the environments 'definition', 'lemma', 'proposition', 'corollary',
% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
% %
% \begin{proof}
% Proofs, examples, and remarks have the initial word in italics,
% while the following text appears in normal font.
% \end{proof}
% For citations of references, we prefer the use of square brackets
% and consecutive numbers. Citations using labels or the author/year
% convention are also acceptable. The following bibliography provides
% a sample reference list with entries for journal
% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
% and a homepage~\cite{ref_url1}. Multiple citations are grouped
% \cite{ref_article1,ref_lncs1,ref_book1},
% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{main}
%
% \begin{thebibliography}{8}
% \bibitem{ref_article1}
% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
% 
% \bibitem{ref_lncs1}
% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
% Springer, Heidelberg (2016). \doi{10.10007/1234567890}
% 
% \bibitem{ref_book1}
% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
% Location (1999)
% 
% \bibitem{ref_proc1}
% Author, A.-B.: Contribution title. In: 9th International Proceedings
% on Proceedings, pp. 1--2. Publisher, Location (2010)
% 
% \bibitem{ref_url1}
% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
% Oct 2017
% \end{thebibliography}
